---
title: "Analysis"
author: "Sophie Hensgen"
date: "5/28/2021"
output: html_document
---

```{r setup, include=FALSE}
library(readr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidyr)
library(data.table)
library(sem)
library(reshape2)
library(xtable)
library(psych)
library(stargazer)
library(jtools)
library(plm)
library(lmtest)
library(Matrix)
library(lme4)
library(effects)
library(robotstxt)
library(RSocrata)
library(rlist)
library(pipeR)
library(gtrendsR)
library(lubridate)
library(ggpubr)
library(ggiraph)
library(devtools)
library(ggiraphExtra)
library(ggeffects)
library(systemfonts)
library(broom.mixed)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(tikzDevice)
library(ggtext)
```

## Load Data Set

```{r Loading Data Set, include = FALSE}

df_stigma_wide <- read_csv("df_stigma_wide.csv")
df_stigma_long <- read_csv("df_stigma_long.csv")
df_stigma_pooled <- read_csv("df_stigma_pooled.csv")

```

## Make Factor Variables

```{r Factor Variables, include = FALSE}

## Variables with more than 2 factors

df_stigma_long$gen_infektion_v <- as.factor(df_stigma_long$gen_infektion_v)
df_stigma_long$gen_ethnie_v <- as.factor(df_stigma_long$gen_ethnie_v)
df_stigma_long$gen_alter_v <- as.factor(df_stigma_long$gen_alter_v)
df_stigma_long$gen_beruf_v <- as.factor(df_stigma_long$gen_beruf_v)
df_stigma_long$gen_alter <- as.factor(df_stigma_long$gen_alter)

## Dummy Variables

df_stigma_long$gen_sex_v <- as.factor(df_stigma_long$gen_sex_v)
df_stigma_long$gen_essential_v <- as.factor(df_stigma_long$gen_essential_v)
df_stigma_long$gen_herkunft <- as.factor(df_stigma_long$gen_herkunft) 
df_stigma_long$gen_bund <- as.factor(df_stigma_long$gen_bund)
df_stigma_long$SD100 <- as.factor(df_stigma_long$SD100)
df_stigma_long$gen_schule <- as.factor(df_stigma_long$gen_schule)

```

## Make Factor Variables - Pooled df

```{r Factor Variables - Pooled df, include = FALSE}

## Variables with more than 2 factors

df_stigma_pooled$gen_infektion_v <- as.factor(df_stigma_pooled$gen_infektion_v)
df_stigma_pooled$gen_ethnie_v <- as.factor(df_stigma_pooled$gen_ethnie_v)
df_stigma_pooled$gen_alter_v <- as.factor(df_stigma_pooled$gen_alter_v)
df_stigma_pooled$gen_beruf_v <- as.factor(df_stigma_pooled$gen_beruf_v)
df_stigma_pooled$gen_alter <- as.factor(df_stigma_pooled$gen_alter)

## Dummy Variables

df_stigma_pooled$gen_sex_v <- as.factor(df_stigma_pooled$gen_sex_v)
df_stigma_pooled$gen_essential_v <- as.factor(df_stigma_pooled$gen_essential_v)
df_stigma_pooled$gen_herkunft <- as.factor(df_stigma_pooled$gen_herkunft) 
df_stigma_pooled$gen_bund <- as.factor(df_stigma_pooled$gen_bund)
df_stigma_pooled$SD100 <- as.factor(df_stigma_pooled$SD100)
df_stigma_pooled$gen_schule <- as.factor(df_stigma_pooled$gen_schule)
df_stigma_pooled$type <- as.factor(df_stigma_pooled$type)

```

## Changing Reference Category

```{r Reference Category, include = FALSE}

## Variables with more than 2 factors

df_stigma_long$gen_infektion_v <- relevel(df_stigma_long$gen_infektion_v, ref = 3)
df_stigma_long$gen_beruf_v <- relevel(df_stigma_long$gen_beruf_v, ref = 3)
df_stigma_long$SD100 <- relevel(df_stigma_long$SD100, ref = 2)
df_stigma_long$gen_alter <- relevel(df_stigma_long$gen_alter, ref = 1)
df_stigma_long$gen_ethnie_v <- relevel(df_stigma_long$gen_ethnie_v, ref = 1)

table(df_stigma_long$gen_infektion_v)
```

## Changing Reference Category

```{r Reference Category, include = FALSE}

## Variables with more than 2 factors

df_stigma_pooled$gen_infektion_v <- relevel(df_stigma_pooled$gen_infektion_v, ref = 3)
df_stigma_pooled$gen_beruf_v <- relevel(df_stigma_pooled$gen_beruf_v, ref = 3)
df_stigma_pooled$SD100 <- relevel(df_stigma_pooled$SD100, ref = 2)
df_stigma_pooled$gen_alter <- relevel(df_stigma_pooled$gen_alter, ref = 1)
df_stigma_pooled$gen_ethnie_v <- relevel(df_stigma_pooled$gen_ethnie_v, ref = 1)

table(df_stigma_pooled$gen_infektion_v)
```

###########################################################################################################################################
##                                                                                                                                       ##
##                                                 Regression - Random Intercept                                                         ##
##                                                                                                                                       ##
###########################################################################################################################################

## Cluster Robust Standard Error Test

```{r Cluster Robust Standard Error Test - shortterm, include = FALSE}

## Random Intercept Model - SD Short term

ranin_short_m10 <-  lmer(gen_sds_shortterm ~ 1 + (1 | id), data = df_stigma_long)
summary(ranin_short_m10)

ranin_short_m11 <-  lmer(gen_sds_shortterm ~ gen_infektion_v + gen_ethnie_v + gen_beruf_v + gen_alter_v + gen_sex_v + (1 | id), data = df_stigma_long)
ranin_short_m12 <-  lmer(gen_sds_shortterm  ~ gen_infektion_v + gen_ethnie_v + gen_beruf_v + gen_alter_v + gen_sex_v + gen_infektion_v*gen_ethnie_v + gen_infektion_v*gen_beruf_v + gen_infektion_v*gen_alter_v + (1 | id), data = df_stigma_long)


```

```{r Cluster Robust Standard Error Test - longterm, include = FALSE}

## Random Intercept Model - SD LongTerm

ranin_long_m20 <-  lmer(gen_sds_longterm ~ 1 + (1 | id), data = df_stigma_long)
summary(ranin_long_m20)

ranin_long_m21 <-  lmer(gen_sds_longterm ~ gen_infektion_v + gen_ethnie_v + gen_beruf_v + gen_alter_v + gen_sex_v + (1 | id), data = df_stigma_long)
ranin_long_m22 <-  lmer(gen_sds_longterm ~ gen_infektion_v + gen_ethnie_v + gen_beruf_v + gen_alter_v + gen_sex_v + gen_infektion_v*gen_ethnie_v + gen_infektion_v*gen_beruf_v + gen_infektion_v*gen_alter_v + (1 | id), data = df_stigma_long)

```


```{r Cluster Robust Standard Error Test - pooled, include = FALSE}

## Random Intercept Model - SD LongTerm

ranin_pooled_m30 <-  lmer(gen_sds ~ 1 + (1 | id), data = df_stigma_pooled)
summary(ranin_pooled_m30)

ranin_pooled_m31 <-  lmer(gen_sds ~ type + gen_infektion_v + gen_ethnie_v + gen_beruf_v + gen_alter_v + gen_sex_v + (1 | id), data = df_stigma_pooled)

```


```{r Tables, include = FALSE}

stargazer(ranin_short_m10, ranin_short_m11, ranin_short_m12,
       title = "Regression Table - Random Intercept Model", 
       align = TRUE, 
       type = "text",
       column.labels = c("M1.0", "M1.1", "M1.2"),
       dep.var.labels   = c("Short Term - Social Distance"),
       model.numbers = FALSE,
       keep.stat = c("n", "ll", "aic", "bic"),
       star.char = c("*", "**", "***"),
       star.cutoffs = c(0.05, 0.01, 0.001))

stargazer(ranin_long_m20, ranin_long_m21, ranin_long_m22,
       title = "Regression Table - Random Intercept Model", 
       align = TRUE, 
       type = "text",
       column.labels = c("M1.0", "M1.1", "M1.2"),
       dep.var.labels   = c("Long Term - Social Distance"),
       model.numbers = FALSE,
       keep.stat = c("n", "ll", "aic", "bic"),
       star.char = c("*", "**", "***"),
       star.cutoffs = c(0.05, 0.01, 0.001))

stargazer(ranin_pooled_m30, ranin_pooled_m31, 
       title = "Regression Table - Random Intercept Model", 
       align = TRUE, 
       type = "text",
       column.labels = c("M1.0", "M1.1", "M1.2"),
       dep.var.labels   = c("Combined"),
       model.numbers = FALSE,
       keep.stat = c("n", "ll", "aic", "bic"),
       star.char = c("*", "**", "***"),
       star.cutoffs = c(0.05, 0.01, 0.001))
```

###########################################################################################################################################
##                                                                                                                                       ##
##                                                 Predicted Estimates - Graph                                                           ##
##                                                                                                                                       ##
###########################################################################################################################################

## Predicted Estimate Graph

```{r Hypothesis 1 - predicted Estimates}

## 0. Data set

# head(df_stigma_long) # control data set

## 1. Build linear model 

# 1.1 Build Linear Model DV: SDS Short Term

# ranin_short_m12 # From before

# 1.2 Build Linear Model DV: SDS Long Term

#cranin_long_m22 # From before

## 2. Plot Model

# 2.1 Use ggpredict to calculate the average predicted estimates

pred_short_h1 <- ggpredict(ranin_short_m12, terms = c("gen_infektion_v"), type = "fe", typical = c("typical_value")) # shortterm sds
pred_long_h1 <- ggpredict(ranin_long_m22, terms = c("gen_infektion_v"), type = "fe", typical = c("typical_value")) # longterm sds

# 2.2 Plot the data from 2.1 using ggplot2

# create additional variables to make it easier to combine both graphs
pred_long_h1$SDS <- "Long-Term SD"
pred_short_h1$SDS <- "Short-Term SD"
pred_long_h1$SDS <- as.factor(pred_long_h1$SDS)
pred_short_h1$SDS <- as.factor(pred_short_h1$SDS)
pred_h1 <- rbind(pred_long_h1, pred_short_h1)
pred_h1$x <- as.factor(pred_h1$x)

  
plot_hyp1 <- pred_h1 %>%
  mutate(SDS = fct_relevel(SDS, 
            "Short-Term SD", "Long-Term SD"),
         x = fct_relevel(x,
            "1", "2", "3")) %>%
  ggplot(aes(x = SDS, y = predicted, col = x)) +
  geom_point(size=1.5, position = position_dodge(width = 0.3)) + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width=.02, position = position_dodge(width = 0.3)) +
  scale_color_manual(name = "Infection Status", values=c("#C4C2C1","#E69F00", "#56B4E9"), 
                     labels = c("Currently Infected", "Former Infected", "Not Infected")) +
  labs( x = "Stigmatized Response", y = "Predicted Average Estimates for Social Distance (SD)") +
  theme_minimal()+
      #theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      theme(
      axis.title = element_text(family = 'Times'),
      axis.text.x = element_markdown(family = 'Times'),
      axis.text.y = element_markdown(family = 'Times'),
      legend.text = ggtext::element_markdown(family = 'Times'),
      legend.title = element_markdown(family = 'Times'))
    
    
print(plot_hyp1)
ggsave(filename = "hyp1.pdf", width = 14, height = 10, dpi = 300, units = "cm")

```

### Predicted Estimate Graph - Hypothesis 2

```{r Hypothesis 2 - predicted Estimates}

## 0. Data set

# head(df_stigma_long) # control data set

## 1. Build linear model 

# 1.1 Build Linear Model DV: SDS Short Term

# ranin_short_m12 # From before

# 1.2 Build Linear Model DV: SDS Long Term

#cranin_long_m22 # From before

## 2. Plot Model

# 2.1 Use ggpredict to calculate the average predicted estimates

pred_short_h2 <- ggpredict(ranin_short_m12, terms = c("gen_infektion_v", "gen_ethnie_v"), type = "fe", typical = c("typical_value")) # shortterm sds
pred_long_h2 <- ggpredict(ranin_long_m22, terms = c("gen_infektion_v", "gen_ethnie_v"), type = "fe", typical = c("typical_value")) # longterm sds

# 2.2 Plot the data from 2.1 using ggplot2

# create additional variables to make it easier to combine both graphs

pred_long_h2$SDS <- "Long-Term SD"
pred_short_h2$SDS <- "Short-Term SD"
pred_long_h2$SDS <- as.factor(pred_long_h2$SDS)
pred_short_h2$SDS <- as.factor(pred_short_h2$SDS)
pred_h2 <- rbind(pred_long_h2, pred_short_h2)
#pred_h2$x <- as.factor(pred_h2$x)

plot_hyp2 <- pred_h2 %>%
  mutate(SDS = fct_relevel(SDS, 
            "Short-Term SD", "Long-Term SD"),
         x = fct_relevel(x, 
            "1", "2", "3")) %>% # changed order of categorical variable x
  ggplot(aes(x=group, y=predicted, col=x)) +
      geom_point(size=1.5, position = position_dodge(width = 0.3)) +
      facet_grid(.~SDS) +
      geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width=.02, position = position_dodge(width = 0.3)) +
      xlab("Ethnicity") +
      ylab("Predicted Average Estimates for Social Distance") + 
      scale_x_discrete(labels = c('German','Turkish','Asian')) +
      #scale_color_discrete(name = "Ethnicity", labels = c('German','Turkish','Asian')) +
      scale_color_manual(name = "Infection Status", values=c("#999999", "#E69F00", "#56B4E9"), labels = c('Currently Infected','Former Infected','Not Infected')) +
      theme_minimal() +
      #theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      theme(
      axis.title = element_text(family = 'Times'),
      axis.text.x = element_markdown(family = 'Times'),
      axis.text.y = element_markdown(family = 'Times'),
      legend.text = ggtext::element_markdown(family = 'Times'),
      legend.title = element_markdown(family = 'Times'))

print(plot_hyp2)
ggsave(filename = "hyp2.pdf", width = 14, height = 10, dpi = 300, units = "cm")
```


### Predicted Estimate Graph - Hypothesis 3

```{r Hypothesis 3 - predicted Estimates}

## 0. Data set

# head(df_stigma_long) # control data set

## 1. Build linear model 

# 1.1 Build Linear Model DV: SDS Short Term

# ranin_short_m12 # From before

# 1.2 Build Linear Model DV: SDS Long Term

#cranin_long_m22 # From before

## 2. Plot Model

# 2.1 Use ggpredict to calculate the average predicted estimates

pred_short_h3 <- ggpredict(ranin_short_m12, terms = c("gen_infektion_v", "gen_beruf_v"), type = "fe", typical = c("typical_value")) # shortterm sds
pred_long_h3 <- ggpredict(ranin_long_m22, terms = c("gen_infektion_v", "gen_beruf_v"), type = "fe", typical = c("typical_value")) # longterm sds

# 2.2 Plot the data from 2.1 using ggplot2

# create additional variables to make it easier to combine both graphs
pred_long_h3$SDS <- "Long-Term SD"
pred_short_h3$SDS <- "Short-Term SD"
pred_long_h3$SDS <- as.factor(pred_long_h3$SDS)
pred_short_h3$SDS <- as.factor(pred_short_h3$SDS)
pred_h3 <- rbind(pred_short_h3, pred_long_h3)

plot_hyp3 <- pred_h3 %>%
  mutate(SDS = fct_relevel(SDS, 
            "Short-Term SD", "Long-Term SD"),
         x = fct_relevel(x, 
            "1", "2", "3")) %>% # changed order of categorical variable x
  ggplot(aes(x=group, y=predicted, col=x)) +
      geom_point(size=1.5, position = position_dodge(width = 0.3)) +
      facet_grid(.~SDS) +
      geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width=.02, position = position_dodge(width = 0.3)) +
      xlab("Occupation") +
      ylab("Predicted Average Estimates for Social Distance") + 
      scale_x_discrete(labels = c("Administrative", "Nurse", "Cashier")) +
      #scale_color_discrete(name = "Ethnicity", labels = c('German','Turkish','Asian')) +
      scale_color_manual(name = "Infection Status", values=c("#999999", "#E69F00", "#56B4E9"), labels = c('Currently Infected','Former Infected','Not Infected')) +
      theme_minimal() +
      #theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      theme(
      axis.title = element_text(family = 'Times'),
      axis.text.x = element_markdown(family = 'Times'),
      axis.text.y = element_markdown(family = 'Times'),
      legend.text = ggtext::element_markdown(family = 'Times'),
      legend.title = element_markdown(family = 'Times'))

print(plot_hyp3)
ggsave(filename = "hyp3.pdf", width = 14, height = 10, dpi = 300, units = "cm")
```



### Predicted Estimate Graph - Hypothesis 4

```{r Hypothesis 4 - predicted Estimates}

## 0. Data set

# head(df_stigma_long) # control data set

## 1. Build linear model 

# 1.1 Build Linear Model DV: SDS Short Term

# ranin_short_m12 # From before

# 1.2 Build Linear Model DV: SDS Long Term

#cranin_long_m22 # From before

## 2. Plot Model

# 2.1 Use ggpredict to calculate the average predicted estimates

pred_short_h4 <- ggpredict(ranin_short_m12, terms = c("gen_infektion_v", "gen_alter_v"), type = "fe", typical = c("typical_value")) # shortterm sds
pred_long_h4 <- ggpredict(ranin_long_m22, terms = c("gen_infektion_v", "gen_alter_v"), type = "fe", typical = c("typical_value")) # longterm sds

# 2.2 Plot the data from 2.1 using ggplot2

# create additional variables to make it easier to combine both graphs
pred_long_h4$SDS <- "Long-Term SD"
pred_short_h4$SDS <- "Short-Term SD"
pred_long_h4$SDS <- as.factor(pred_long_h4$SDS)
pred_short_h4$SDS <- as.factor(pred_short_h4$SDS)
pred_h4 <- rbind(pred_short_h4, pred_long_h4)

# create additional variables to make it easier to combine both graphs

plot_hyp4 <- pred_h4 %>%
  mutate(SDS = fct_relevel(SDS, 
            "Short-Term SD", "Long-Term SD"),
         x = fct_relevel(x, 
            "1", "2", "3")) %>% # changed order of categorical variable x
  ggplot(aes(x=group, y=predicted, col=x)) +
      geom_point(size=1.5, position = position_dodge(width = 0.3)) +
      facet_grid(.~SDS) +
      geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width=.02, position = position_dodge(width = 0.3)) +
      xlab("Age") +
      ylab("Predicted Average Estimates for Social Distance") + 
      scale_x_discrete(labels = c("22 Years", "43 Years", "64 Years")) +
      #scale_color_discrete(name = "Ethnicity", labels = c('German','Turkish','Asian')) +
      scale_color_manual(name = "Infection Status", values=c("#999999", "#E69F00", "#56B4E9"), labels = c('Currently Infected','Former Infected','Not Infected')) +
      theme_minimal() +
      #theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      theme(
      axis.title = element_text(family = 'Times'),
      axis.text.x = element_markdown(family = 'Times'),
      axis.text.y = element_markdown(family = 'Times'),
      legend.text = ggtext::element_markdown(family = 'Times'),
      legend.title = element_markdown(family = 'Times'))
      
print(plot_hyp4)
ggsave(filename = "hyp4.pdf", width = 14, height = 10, dpi = 300, units = "cm")
```


```{r Clean Up}

rm(plot_hyp1, plot_hyp2, plot_hyp3, plot_hyp4, pred_h1, pred_h2, pred_h3, pred_h4, pred_long_h1, pred_long_h2, pred_long_h3, pred_long_h4, pred_short_h1, pred_short_h2, pred_short_h3, pred_short_h4, ranin_long_m20, ranin_long_m21, ranin_long_m22, ranin_pooled_m31, ranin_pooled_m30, ranin_short_m10, ranin_short_m11, ranin_short_m12)

```


















